Copy number inference with InferCNV

### 2024-07-17 analyses/cell-type-ewings/template_notebooks/cnv-workflow/04-infercnv.Rmd
fix up some of the ewings files with diffs

```{r}
# get a dataframe with barcodes, sum_classification and cluster_classification 
celltypes_df <- cnv_df |> 
  dplyr::select(
    barcodes,
    cnv_proportion_classification = cnv_mean_classification,
    cnv_sum_classification = cnv_classification
  )

>>>>

```{r}
# get a dataframe with barcodes, sum_classification and cluster_classification
celltypes_df <- cnv_df |>
  dplyr::select(
    barcodes,
    cnv_proportion_classification = cnv_mean_classification,
    mean_cnv_proportion = mean_proportion
  )
